Designing for Complex Gig Work and Careers

### 2017-03-06 proposals/SIGFproposal_2017/old_cyber.tex
sigf17

\section*{Relationship to previously funded work:}
PIs Bernstein,
Levi,
Johari and Valentine have an ongoing funded Cyber project titled ``Cyber Work: The Future of Networked Labor".
This project outlined major goals:
\begin{inlinelist}
\item ethnographic studies of online work practice,
\item the creation of crowd organizations,
\item collective action,
and
\item new labor platforms
\end{inlinelist}.
The project was scoped too ambitiously for the funding available last year,
requesting \$1.2 million over three years.
Thus, we have split out part of
(1) and all of
(3) into this separate proposal.
(2) and (4) are making rapid progress under the existing funding,
and currently have significant publications in preparation and under review,
as well as an alpha version of the platform launched.
If the committee wishes to fund this proposal,
we are comfortable with either pitching it as a separate proposal or folding it into the existing Cyber Work proposal as part of a renewal request.
The timing of the funding start date is flexible.

@@

Second, we will create and launch a cooperatively owned ``gig" marketplace for domestic workers in collaboration with the National Domestic Workers Alliance
(NDWA).
Our own prior work established a collective action platform for crowd workers
\cite{dynamo}.
We now seek to augment this exploration of union--style collective by creating a cooperative that can scale up and set its own standards in the marketplace.
The NDWA's Fair Care Labs are providing access to interested domestic workers
(house cleaners), and we are designing and implementing the platform with them as a pilot group.
The goal is to understand how to design for a set of distributed workers to achieve consensus on issues such as management, service fees, and arbitration.

@@

% Together with the Fair Care Labs, we are designing and launching a cooperative gig labor market for domestic workers
% (house cleaners).
% This cooperative labor market, Alia, is designed for domestic workers in the California Bay Area.
% However, our interest
% (and Fair Care Labs')
% is to generalize its insights to other workers and industries.
% While the driving domain is already crowded with services such as Lyft and Uber, domestic work is a more ideal area to launch a research prototype.
% In addition, the NDWA Fair Care Labs' support and network will help us gain rapid traction.
% The web and mobile application, Alia, enables the basic affordances of ``gig" work for domestic work 
% --- rapid scheduling of any available worker in the network
% (Figure 1)

@@

\bibliographystyle{apalike}
\bibliography{../references.bib}
\end{document}

>>>>

\section*{Relationship to previously funded work:}
PIs Bernstein,
Levi,
Johari and Valentine have an ongoing funded Cyber project titled ``Cyber Work: The Future of Networked Labor''.
This project outlined major goals:
\begin{inlinelist}
\item ethnographic studies of online work practice,
\item the creation of crowd organizations,
\item collective action,
and
\item new labor platforms
\end{inlinelist}.
The project was scoped too ambitiously for the funding available last year,
requesting \$1.2 million over three years.
Thus, we have split out part of
(1) and all of
(3) into this separate proposal.
(2) and (4) are making rapid progress under the existing funding,
and currently have significant publications in preparation and under review,
as well as an alpha version of the platform launched.
If the committee wishes to fund this proposal,
we are comfortable with either pitching it as a separate proposal or folding it into the existing Cyber Work proposal as part of a renewal request.
The timing of the funding start date is flexible.

@@

Second, we will create and launch a cooperatively owned ``gig'' marketplace for domestic workers in collaboration with the National Domestic Workers Alliance
(NDWA).
Our own prior work established a collective action platform for crowd workers
\cite{dynamo}.
We now seek to augment this exploration of union--style collective by creating a cooperative that can scale up and set its own standards in the marketplace.
The NDWA's Fair Care Labs are providing access to interested domestic workers
(house cleaners), and we are designing and implementing the platform with them as a pilot group.
The goal is to understand how to design for a set of distributed workers to achieve consensus on issues such as management, service fees, and arbitration.

@@

% Together with the Fair Care Labs, we are designing and launching a cooperative gig labor market for domestic workers
% (house cleaners).
% This cooperative labor market, Alia, is designed for domestic workers in the California Bay Area.
% However, our interest
% (and Fair Care Labs')
% is to generalize its insights to other workers and industries.
% While the driving domain is already crowded with services such as Lyft and Uber, domestic work is a more ideal area to launch a research prototype.
% In addition, the NDWA Fair Care Labs' support and network will help us gain rapid traction.
% The web and mobile application, Alia, enables the basic affordances of ``gig'' work for domestic work 
% --- rapid scheduling of any available worker in the network
% (Figure 1)

@@

\bibliographystyle{apalike}
\bibliography{references.bib}
\end{document}
